\thetitle

### 2020-08-10 writing/mutate.tex
Add subsection describing selection of debugging scenarios

So far we have established that our mutators and~\citet{gtnffvf-jfp-2019}'s 
benchmarks are sufficient to create a large number of realistic ill-typed Type Racket
programs. However, in an ill-typed program with correct types, like
in our case, it is trivial to figure out which component contains the bug.
It is the component that doesn't type check. Thus the ill-typed mutants
do not offer an interesting setting to try out the debugging abilities of
rational programmers. That said, we can derive interesting debugging
scenarios by removing type specifications from some of the components of
the benchmarks. The resulting mix-typed programs may be well-typed and when
run may raise a type error. Section~\ref{sec:rational} explains how we can
explore the space of debugging scenarios in a principled manner. As a
final remark in this section, with the data from
figure~\ref{fig:mutators-runtime-hit}, we verify  that in each of the three semantics
we target, between 25\% and
90\% of the ill-typed mutants each mutator generates give rise to at least one interesting debugging scenario.

>>>>

So far we have established that our mutators and~\citet{gtnffvf-jfp-2019}'s 
benchmarks are sufficient to create a large number of realistic ill-typed Typed Racket
programs. However, in an ill-typed program with correct types, like
in our case, it is trivial to figure out which component contains the bug.
It is the component that doesn't type check. Thus the ill-typed mutants
do not offer an interesting setting to try out the debugging abilities of
rational programmers. That said, we can derive interesting debugging
scenarios by removing type specifications from some of the components of
the benchmarks. The resulting mix-typed programs may be well-typed and when
run may raise a type error. Section~\ref{sec:rational} explains how we can
explore the space of debugging scenarios in a principled manner. As a
final remark in this section, with the data from
figure~\ref{fig:mutators-runtime-hit}, we verify  that in each of the three semantics
we target, between 25\% and
90\% of the ill-typed mutants each mutator generates give rise to at least one interesting debugging scenario.

### 2020-08-10 writing/rational.tex
Add subsection describing selection of debugging scenarios

>>>>

\subsection{Where do the trails begin?}
The above descriptions of blame trails under various modes all assume that every trail has a beginning scenario.
How we select the scenarios from which the trails start has ramifications for the kinds of results we can find, and what we can learn from them.
We break this decision into three basic factors, each of which specify an element of the selection.

First, not all debugging scenarios are suitable for evaluating blame across all three semantics.
For instance, there exist scenarios where Natural's checks discover a problem but Transient and Erasure do not.
Since Transient and Erasure provide no debugging information (and in particular no blame) in such cases, we have nothing to evaluate.
As alluded to in the previous paragraph, scenarios where the type checker detects the problem statically are also uninteresting.
Hence, we select only scenarios which are interesting in all three semantics.
We can do this simply by leveraging~\citet{??? Ben}'s proof that a dynamic type error in erasure implies a dynamic type error in both Transient and Natural, to only look at scenarios in which Erasure detects the problem.
In other words, we consider just those debugging scenarios that are interesting under Erasure.

The second factor is that we would like to be able to compare the behavior of blame between each of our three semantics.
In order to do so, we must evaluate each of the semantics on the same set of scenarios;
this allows us to compare for any given scenario how Natural compares to Erasure, for instance.
Hence, we pre-select a sample of scenarios which serve as the starting points to evaluate all three semantics.

Finally, the third factor is that we only want to consider debugging scenarios in which the bug has effects that cross component boundaries.
In the context of migratory typing, dynamic type enforcement occurs when values cross component boundaries.
However, a bug may be caught by the runtime before any values it influences flow out of the containing component -- for instance, if the bug is that a direct argument to \texttt{+} becomes a string.
We consider such scenarios trivial, becase typing the component in which the problem manifests immediately identifies that same component as the buggy one.
In an effort to avoid these trivial scenarios, we further restrict our sample of debugging scenarios to only those in which the stack trace from Erasure identifies a component other than the buggy one.
Those scenarios may yet be trivial in the other two semantics -- with more checking and blame tracking -- but this selection ensures that none of our scenarios are trivial ``a priori''.
